\documentclass[twoside]{Style/uva-inf-bachelor-thesis}
\usepackage[english]{babel}
\usepackage{csquotes}
% For drawing images and graphs
\usepackage{tikz}

% For  resizing tables
\usepackage{adjustbox}

% References
\usepackage[
    maxbibnames=10,
    style=authoryear-comp,
    urldate=comp
]{biblatex}
\addbibresource{references.bib}
% For hyperref cite
\DeclareCiteCommand{\citeyear}
    {}
    {\bibhyperref{\printfield{year}}}
    {\multicitedelim}
    {}

\DeclareCiteCommand{\citeyearpar}
    {}
    {\mkbibparens{\bibhyperref{\printfield{year}}}}
    {\multicitedelim}
    {}

% Used for different math equations
\usepackage{amssymb}
\usepackage{amsmath}

% Package for the images and the subfiles of sections
\usepackage{graphicx}
\graphicspath{Images/}
\usepackage{floatrow}% Table float box with bottom caption, box width adjusted to content
\usepackage{multirow}
\newfloatcommand{capbtabbox}{table}[][\FBwidth]

% For multiple images
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig}

% For placing footnotes at the bottom
\usepackage[bottom]{footmisc}
\interfootnotelinepenalty=10000

% For code listings
\usepackage{listings}
% listing for JSON, from https://tex.stackexchange.com/questions/83085/how-to-improve-listings-display-of-json-files
\colorlet{punct}{red!60!black}
\definecolor{background}{HTML}{EEEEEE}
\definecolor{delim}{RGB}{20,105,176}
\colorlet{numb}{magenta!60!black}

\lstdefinelanguage{JSON}{
    basicstyle=\normalfont\ttfamily,
    numbers=left,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
    backgroundcolor=\color{background},
    literate=
     *{0}{{{\color{numb}0}}}{1}
      {1}{{{\color{numb}1}}}{1}
      {2}{{{\color{numb}2}}}{1}
      {3}{{{\color{numb}3}}}{1}
      {4}{{{\color{numb}4}}}{1}
      {5}{{{\color{numb}5}}}{1}
      {6}{{{\color{numb}6}}}{1}
      {7}{{{\color{numb}7}}}{1}
      {8}{{{\color{numb}8}}}{1}
      {9}{{{\color{numb}9}}}{1}
      {:}{{{\color{punct}{:}}}}{1}
      {,}{{{\color{punct}{,}}}}{1}
      {\{}{{{\color{delim}{\{}}}}{1}
      {\}}{{{\color{delim}{\}}}}}{1}
      {[}{{{\color{delim}{[}}}}{1}
      {]}{{{\color{delim}{]}}}}{1},
    morestring=[b]"
}
\lstdefinelanguage{Cplusplus}{
    basicstyle=\normalfont\ttfamily,
    numbers=left,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    breakatwhitespace=true,
    keepspaces=true,
    keywordstyle=\color{blue},
    frame=lines,
    backgroundcolor=\color{background},
    morestring=[b]"
}
% Change references to subsection level
\setcounter{secnumdepth}{3} % default value for 'report' class is "2"

%----Helper code for dealing with external references----
% (by cyberSingularity at http://tex.stackexchange.com/a/69832/226)
% https://www.overleaf.com/learn/how-to/Cross_referencing_with_the_xr_package_in_Overleaf
\usepackage{xr}
\makeatletter

\newcommand*{\addFileDependency}[1]{% argument=file name and extension
    \typeout{(#1)}% latexmk will find this if $recorder=0 however, in that case, it will ignore #1 if it is a .aux or .pdf file etc and it exists! If it doesn't exist, it will appear in the list of dependents regardless)%

    \@addtofilelist{#1} % Write the following if you want it to appear in \listfiles, although not really necessary and latexmk doesn't use this

    \IfFileExists{#1}{}{\typeout{No file #1.}} % latexmk will find this message if #1 doesn't exist (yet)
}\makeatother

\newcommand*{\myexternaldocument}[1]{%
    \externaldocument{#1}%
    \addFileDependency{#1.tex}%
    \addFileDependency{#1.aux}%
}
%------------End of helper code--------------
\graphicspath{Images/}
\usepackage{subfiles}

% Title Page
% \title{Energy efficient SNNI, a comparison between Cheetah and CryptFlow2 [or] Moving to energy efficient SNNI, a comparison between Cheetah and CryptFlow2 [or] Progressing to energy efficient SNNI, a comparison between Cheetah and Cryptflow2}
% \title{Progressing to energy efficient SNNI, a comparison between Cheetah and CryptFlow2}
% \title{Progressing to energy efficient SNNI, the impact of bandwidth on Cheetah and CryptFlow2}
% \title{Energy efficient Secure Neural Network Inference: investigating effects of bandwidth on approaches Cheetah and CrypTFlow2}
\title{Energy efficient Secure \\Neural Network Inference
\\\large The effects of Bandwidth on the Energy Consumption}
\author{Jorit Prins}
\supervisors{Zoltan Mann}
% \signedby{Signees}

\begin{document}
\maketitle

\begin{abstract}
The use of Machine Learning (ML) typically consists of two phases: training and inference. The training phase is an tedious and time exhausting process. In Machine Learning as a Service, a company or other party offers a pre-trained Neural Network (NN) to the client. MLaaS can offer privacy threats for both the client and the server. Secure Neural Network Inference (SNNI) entails the problem of a client learning the output of a NN held by a server, without the server learning the input and the client about the NN. No approach has been widely accepted, but some proof of concept approaches have been suggested. These approaches are only tested on accuracy and efficiency, while other metrics, like energy consumption are not tested, although they are still of importance. In this thesis, I test how much energy Cheetah consumes compared to its counterpart CrypTFlow2, two of the most recent approaches, and how the bandwidth influences the energy consumption. In this research, I found that there are not many approaches to measure the energy consumption of programs. I did find Scaphandre, and used it to measure the power consumption of Cheetah and CrypTFlow2. I found that Cheetah is not only faster, but also used less power compared to CrypTFlow2. Additionally, I found that the improvement increases when limiting the bandwidth of the client. Energy consumption increases after a certain turn-point.
% \color{red}Draft\color{red}
% \begin{itemize}
%     \item MLaaS can offer privacy threats for both client and server
%     \item SNNI is a solution
%     \item No widely accepted approach found
%     \item Proof-of-concepts only tested on efficiency and accuracy and not on power/energy consumption, while this is still important
%     \item \textit{write about findings of research}
% \end{itemize}
% \color{red}End of draft\color{red}

\end{abstract}

\tableofcontents

\chapter{Introduction}\label{chap:introduction}
\subfile{Sections/1_Introduction}

\chapter{Theoretical background}\label{chap:theoreticalbackground}
\subfile{Sections/2_TheoreticalBackground}

\chapter{My work}\label{chap:mywork}
\subfile{Sections/3_Code}

\chapter{Experimental results}\label{chap:experiments}
\subfile{Sections/4_ExperimentalResults}

\chapter{Discussion}\label{chap:discussion}
\subfile{Sections/5_Discussion}

\chapter{Conclusion}\label{chap:conclusion}
\subfile{Sections/6_Conclusion}

\printbibliography
\end{document}
